Scikit-learn: machine learning without learning the machinery

### 2014-11-06 article.tex
actually n-grams aren't that interesting
nurturing section: stress code review over version control

@@

The greatest asset of the scikit-learn project is its breadth of
contributors, coming from different backgrounds, working in different
institutions, with a variety of applications: more than 200 contributors in
total, 15 active core contributors in the past year. Indeed, not only
is there strength in numbers, but also the convergence of points of views
make better code and better design. From a developer's perspective, the
project is managed with the goals of enabling newcomers to
contribute while keeping a high quality assurance. For these purposes, we
rely heavily on GitHub (\url{http://github.com}) with an online
development workflow relying on distributed version control using git,
and intensive code review. The code review process is a great asset to
raising the quality of the code, from all points of view: algorithmic,
numerical robustness, homogeneity of APIs, ease of use, documentation.
Another central aspect for quality in the project is the heavy use of
unit testing (up to 88\% of the lines of code are covered), run
continuously on all contributions thanks to the Travis platform
(\url{http://travis-ci.org}).

>>>>

We see that the expected accuracy is about 88\%.
Experimenting with different classification models is easy:
e.g., replacing \texttt{LogisticRegression} with \texttt{svm.LinearSVC}
gives a linear support vector machine.

@@

The greatest asset of the scikit-learn project is its breadth of
contributors, coming from different backgrounds, working in different
institutions, with a variety of applications: more than 200 contributors in
total, 15 active core contributors in the past year. Indeed, not only
is there strength in numbers, but the convergence of points of views
make for better code and better design. From a developer's perspective, the
project is managed with the goal of enabling newcomers to contribute,
while keeping quality high.

Our development workflow relies on intensive code review,
facilitated by the online version control environment GitHub (\url{http://github.com})
The code review process is a great asset to
raising the quality of the code, from all points of view: algorithmic,
numerical robustness, homogeneity of APIs, ease of use, documentation.
Another central aspect for quality in the project is the heavy use of
unit testing (up to 88\% of the lines of code are covered), run
continuously on all contributions thanks to the Travis platform
(\url{http://travis-ci.org}).
